\vspace{-2.0cm}Stuff

### 2014-05-26 report/draft.tex
Report Staging

\begin{document}
\begingroup  
  \centering
  \LARGE Master's Report - Draft\\[1em]
  \large Matt Edwards\\
  11 May 2014\par
\endgroup
\texttt{NOTE TO (maybe) FIX: I've been using POint Transect and VCP interchangeably, Buckland makes a distinction (2004, pg 6) that Point Transect you only survey the area immediately around the point, where as VCP, you are censusing $\pi w^2$. However, in the 2006 paper, he refers to them interchangeably.}
\section{Introduction}
Transects, both point and line, are a method of population density estimation often used in the ecological sciences. They are useful when populations are too small to be seen from the air (birds, rodents) or may be masked by the canopy (ground plants.) Recent studies that use distance sampling include Norwegian bird populations (Pedersen et al. 2012), Komodo dragon prey estimates (Ariefiandy et al. 2013), Serengeti carnivore abundance (Durant et al. 2011), and estimates for butterfly populations (Isaac et al. 2011). A study by Cox et al. extends point transect sampling for use with underwater acoustics for estimates of krill populations (2011), and a study by Rowcliffe et al. combines distance sampling with camera traps to estimate populations (2011).

>>>>

\begin{document}
\begingroup  
  \centering
  \LARGE Master's Report - Draft\\[1em]
  \large Matt Edwards\\
  11 May 2014\par
\endgroup
\texttt{NOTE TO (maybe) FIX: I've been using Point Transect and VCP interchangeably, Buckland makes a distinction (2004, pg 6) that Point Transects you only survey the area immediately around the point, where as VCP, you are censusing $\pi w^2$. However, in the 2006 paper, he refers to them interchangeably.}
\section{Introduction}
Transects, both point and line, are a method of population density estimation often used in the ecological sciences. They are useful when populations are too small to be seen from the air (birds, rodents) or may be masked by the canopy (ground plants.) Recent studies that use distance sampling include Norwegian bird populations (Pedersen et al. 2012), Komodo dragon prey estimates (Ariefiandy et al. 2013), Serengeti carnivore abundance (Durant et al. 2011), and estimates for butterfly populations (Isaac et al. 2011). A study by Cox et al. extends point transect sampling for use with underwater acoustics for estimates of krill populations (2011), and a study by Rowcliffe et al. combines distance sampling with camera traps to estimate populations (2011).
